---
output: 
  github_document:
    html_preview: false
---

# vebmedr

[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/vembedr)](https://cran.r-project.org/package=vembedr)
[![Travis-CI Build Status](https://travis-ci.org/ijlyttle/vembedr.svg?branch=master)](https://travis-ci.org/ijlyttle/vembedr)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)

```{r, echo = FALSE}
library("htmltools")
library("vembedr")

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

The goal of the vembedr package is to make it a little bit easier for you to embed videos into your **rmarkdown** documents and your **shiny** apps. Three services are currently supported: YouTube, Vimeo, and Microsoft Channel 9 (including UseR! 2016 and 2017 videos).

## New to version 0.1.3

- updates README to show some custom formatting, thanks [Eric Koncina](https://github.com/koncina) and [Aurélien Ginolhac](https://github.com/ginolhac)
- adds function `embed_user2017()`: embed videos from UseR!2017

## Installation

You can install the latest released version from CRAN with:

```{r eval=FALSE}
install.packages("vembedr")
```

or the latest development version from GitHub with:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("ijlyttle/vembedr")
```

### Documentation

This project supports two documentation-websites, built using [pkgdown](https://pkgdown.r-lib.org):

- [CRAN version](https://ijlyttle.github.io/vembedr)
- latest [developent version](https://ijlyttle.github.io/vembedr/dev) from GitHub

## Examples

For these examples, it can be useful to load the **htmltools** package along with the **vembedr** package.

```{r}
library("htmltools")
library("vembedr")
```

With the function `embed_url()`, you can use the URL from your browser to embed video:

```{r}
embed_url("https://www.youtube.com/watch?v=uV4UpCq2azs")
```

-----

If you just want the embedding code, the `suggest_embed()` function may be useful:

```{r}
suggest_embed("https://youtu.be/uV4UpCq2azs?t=1m32s")
```

All of the features shown here can be used for all the supported services: YouTube, Vimeo, and Channel 9. Here, the features are mixed-and-matched in the interest of brevity.

-----

To embed a YouTube (or Vimeo, or Channel 9) video you can use its identifier, which you can get from the original URL. 

```{r}
embed_youtube("1-vcErOPofQ")
```

-----

For this example, we embed a Vimeo using some custom formatting - thanks to [Eric Koncina](https://github.com/koncina) and [Aurélien Ginolhac](https://github.com/ginolhac) who [showed the way](https://github.com/ijlyttle/vembedr/issues/25). First let's introduce some css where we can define some rounded corners for an embedded video, by describing an HTML class, `vembedr`:

```{css}
.vembedr {
  display: inline-block;
  border-radius: 25px; /* adjust it to your needs */
  overflow: hidden;
}

.vembedr iframe {
  display: block;
  border: none;
}
```

    ```{css}
    .vembedr {
      display: inline-block;
      border-radius: 25px; /* adjust it to your needs */
      overflow: hidden;
    }
    
    .vembedr iframe {
      display: block;
      border: none;
    }
    ```

To embed a Vimeo with some custom formatting:

- call `embed_vimeo()` using the Vimeo identifier, *then*
- wrap that in `<div/>` using our new `vembedr` class, *then*
- wrap that in a `<div/>` that centers its contents

```{r}
embed_vimeo("189919038") %>%
  div(class = "vembedr") %>%
  div(align = "center")
```

```{r echo=FALSE}
tags$br()
```

Of course, the use of the pipe operator is optional. Hat tip to Karthik Ram for [tweeting](https://twitter.com/_inundata/status/794616331727294464) out this Vimeo.

-----

You can also specify a start time. Please note that for Vimeo, specifying a start time implies that the video **will** be auto-played (which can be annoying).

Here's an example using a lightning presentation from UseR!2017:

```{r}
embed_user2017("Room-202-Lightning-Talks") %>% 
  use_start_time("26m35s")
```

------


## Note for GitHub README and RStudio viewer

The GitHub Markdown renderer does not support video embedding. To see everything in action, you are invited to visit the [GitHub pages](http://ijlyttle.github.io/vembedr/) site, built using [pkgdown](http://hadley.github.io/pkgdown/).

If you use the RStudio-IDE viewer to preview your work, please note that RStudio have made the design choice not to allow arbitrary external web-content in the IDE, which is wholly appropriate. However, with the advent of the [learnr](https://rstudio.github.io/learnr/) package, the IDE-viewer supports embedding of Vimeo and YouTube videos.

Otherwise, you can simply open your preview in an external browser.

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
