---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
library("htmltools")
library("vembedr")

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

The functions in this package make it a little bit easier for you to embed hosted videos into your RMarkdown documents and Shiny apps.

## Installation

You may install the latest development version from github by:

```{r eval=FALSE}
if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}
devtools::install_github("ijlyttle/vembedr")
```

# Use

It's fairly simple, you just need the video id from either Vimeo or YouTube. In RMarkdown, you may wish to set the alignment of the code chunk.

```{r eval=FALSE}
embed_vimeo("45196609")
```

```{r eval=FALSE}
embed_youtube("dQw4w9WgXcQ")
```

Embedding does not work for the standard Github site, but it does for `gh-pages`.

# Future work

Both YouTube and Vimeo support the use of query parameters in the URL. Supporting this is the likely next step. 

* [Vimeo embedding](https://developer.vimeo.com/player/embedding)
* [YouTube embedding](https://developers.google.com/youtube/player_parameters)

At some point, I'd like to submit this to CRAN, so your feedback will be very welcome.

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
