---
output: 
  github_document:
    html_preview: false
---

# vebmedr

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/vembedr)](http://cran.r-project.org/package=vembedr)
[![Travis-CI Build Status](https://travis-ci.org/ijlyttle/vembedr.svg?branch=master)](https://travis-ci.org/ijlyttle/vembedr)
[![Coverage Status](https://img.shields.io/codecov/c/github/ijlyttle/vembedr/master.svg)](https://codecov.io/github/ijlyttle/vembedr?branch=master)

```{r, echo = FALSE}
library("htmltools")
library("vembedr")

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

The goal of the vembedr package is to make it a little bit easier for you to embed videos into your **rmarkdown** documents and your **shiny** apps. Three services are currently supported: YouTube, Vimeo, and Microsoft Channel 9 (including UseR! 2016 videos).

## New to version 0.1.2

- New function, `suggest_embed()`, given a URL from a video's web-page: suggests embedding-code. 

## Installation

You can install the latest released version from CRAN with

```{r eval=FALSE}
install.packages("vembedr")
```

or the latest development version from github with

```{r eval=FALSE}
if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}
devtools::install_github("ijlyttle/vembedr")
```

## Note for GitHub README and RStudio viewer

The GitHub Markdown renderer does not support video embedding. To see everything in action, you are invited to visit the [GitHub pages](http://ijlyttle.github.io/vembedr/) site, built using [pkgdown](http://hadley.github.io/pkgdown/).

If you use the RStudio-IDE viewer to preview your work, please note that RStudio have made the design choice not to allow arbitrary external web-content in the IDE, which is wholly appropriate. Simply open your preview in an external browser.

## Examples

For these examples, it can be useful to load the **htmltools** package along with the **vembedr** package.

```{r}
library("htmltools")
library("vembedr")
```

All of the features shown here can be used for all the supported services: YouTube, Vimeo, and Channel 9. Here, the features are mixed-and-matched in the interest of brevity.

To embed a YouTube (or Vimeo, or Channel 9) video you can:

- Use its identifier, which you can get from the original URL. 
- To have the code suggested, you can use `suggest_embed()` using the video's URL.
- You can embed directly using its URL.

```{r eval=FALSE}
embed_youtube("1-vcErOPofQ")
```

```{r}
suggest_embed("https://www.youtube.com/watch?v=1-vcErOPofQ")
```

```{r}
embed_url("https://www.youtube.com/watch?v=1-vcErOPofQ")
```

Similarly, to embed a Vimeo, use its identifier. Note that we can apply some formatting by wrapping the output of the `embed_vimeo()` function in an **htmltools** `div()`.

```{r}
div(
  align = "center",
  embed_vimeo("189919038")
)
```

Hat tip to Karthik Ram for [tweeting](https://twitter.com/_inundata/status/794616331727294464) out this Vimeo.

For YouTube, Vimeo, and Microsoft Channel 9 (hosts of the User! 2016 videos) you can specify a start time. Please note that for Vimeo, specifying a start time implies that the video **will** be auto-played (which can be annoying).

Here's an example using a lightning presentation from UseR! 2016:

```{r}
embed_user2016("Day-3-Siepr-130-Ligtning-Talks-100-PM-140-PM") %>% 
  use_start_time("21m45s")
```


## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
