---
output: 
  github_document:
    html_preview: false
always_allow_html: true    
---

# vembedr

  <!-- badges: start -->
  [![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/vembedr)](https://cran.r-project.org/package=vembedr)
  [![R build status](https://github.com/ijlyttle/vembedr/workflows/R-CMD-check/badge.svg)](https://github.com/ijlyttle/vembedr/actions)
  [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
  <!-- badges: end -->
  
```{r, echo = FALSE}
library("htmltools")
library("vembedr")

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

The goal of the vembedr package is to make it a little bit easier for you to embed videos into your **rmarkdown** documents and your **shiny** apps. Four services are currently supported:

- YouTube 
- Vimeo
- Microsoft Channel 9 (including UseR! 2016 and 2017 videos).
- Box

## New to version 0.1.3.9000

- functions to help you format: `use_rounded()`, `use_align()`, and `use_bs_responsive()`.
- you can embed videos hosted on Box, using `embed_box()`.

## Installation

You can install the latest released version from CRAN with:

```{r eval=FALSE}
install.packages("vembedr")
```

or the latest development version from GitHub with:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("ijlyttle/vembedr")
```

### Documentation

This project supports two documentation-websites, built using [pkgdown](https://pkgdown.r-lib.org):

- [CRAN version](https://ijlyttle.github.io/vembedr)
- latest [developent version](https://ijlyttle.github.io/vembedr/dev) from GitHub

## Examples

For these examples, it can be useful to load the **htmltools** package along with the **vembedr** package.

```{r eval=FALSE}
library("vembedr")
```

With the function `embed_url()`, you can use the URL from your browser to embed video:

```{r}
embed_url("https://www.youtube.com/watch?v=uV4UpCq2azs")
```

-----

If you just want the embedding code, the `suggest_embed()` function may be useful:

```{r}
suggest_embed("https://youtu.be/uV4UpCq2azs?t=1m32s")
```

All of the features shown here can be used for all the supported services: YouTube, Vimeo, and Channel 9. Here, the features are mixed-and-matched in the interest of brevity.

-----

To embed a YouTube (or Vimeo, or Channel 9) video you can use its identifier, which you can get from the original URL. 

```{r}
embed_youtube("lGTEUtS5H7I")
```

-----

For this example, we embed a Vimeo using some custom formatting - thanks to [Eric Koncina](https://github.com/koncina) and [Aurélien Ginolhac](https://github.com/ginolhac) who [showed the way](https://github.com/ijlyttle/vembedr/issues/25). You can use the function `use_align()`:


```{r}
embed_vimeo("189919038") %>%
  use_align("center")
```

Of course, the use of the pipe operator is optional. Hat tip to Karthik Ram for [tweeting](https://twitter.com/_inundata/status/794616331727294464) out this Vimeo.

-----

You can also specify a start time. Please note that for Vimeo, specifying a start time implies that the video **will** be auto-played (which can be annoying).

Here's an example using a lightning presentation from UseR!2017:

```{r}
embed_user2017("Room-202-Lightning-Talks") %>% 
  use_start_time("26m35s")
```

One of the more-frustrating things I have noticed while developing this package, is that more-and-more videos will not play when embedded at a different site (like your RMarkdown document). This is due to licensing issues. I am all for the copyright holder being able to specify where there content can and cannot be played; I just wish they could make this more obvious when looking for videos to demonstrate.

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
