---
output: 
  github_document
---

# vembedr

  <!-- badges: start -->
  [![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/vembedr)](https://cran.r-project.org/package=vembedr)
  [![R-CMD-check](https://github.com/ijlyttle/vembedr/workflows/R-CMD-check/badge.svg)](https://github.com/ijlyttle/vembedr/actions)
  <!-- badges: end -->
  
```{r, echo = FALSE}
library("htmltools")
library("vembedr")

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

The goal of vembedr is to make it a little bit easier for you to embed videos into your **RMarkdown** documents and your **Shiny** apps. 
In this verison, five services are supported:

- YouTube 
- Vimeo
- Box
- Microsoft Stream

## New to version 0.1.5

- updated embedding code to comport with new Pandoc.
- deprecated Microsoft Channel 9 (including UserR! 2016 & 2017)), as service is deprecated.

## Installation

You can install the latest released version from CRAN with:

```{r eval=FALSE}
install.packages("vembedr")
```

or the latest development version from GitHub with:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("ijlyttle/vembedr")
```

## Documentation

This project supports two documentation-websites, built using [pkgdown](https://pkgdown.r-lib.org):

- [CRAN version](https://ijlyttle.github.io/vembedr/)
- latest [developent version](https://ijlyttle.github.io/vembedr/dev/) from GitHub

### Usage

The most useful function might be `embed_url()`. 
If the URL is from one of the supported services, it will do the right thing:

```r
library("vembedr")

embed_url("https://www.youtube.com/watch?v=uV4UpCq2azs")
```

The video is not embedded in this README file as is rendered to Markdown; to see embedded videos, please see `vignette("vembedr")`. Each of the supported services, e.g. YouTube, is discussed in `vignette("embed")`. 

The functions are designed to be piped. 
For example, here's how you can modify the appearance and the start time:

```r
embed_url("https://www.youtube.com/watch?v=uV4UpCq2azs") %>%
  use_start_time("1m32") %>%
  use_align("center")
```

To see these functions in action, see `vignette("modify")`.

### Caveats

 - Be aware that, due to licensing issues, not all videos will play when embedded at a different site (like your HTML document).

 - The RStudio viewer will embed YouTube and Vimeo videos, but not others. 
   Videos from all services should be rendered as you expect in a browser like Chrome.
   
 - Some of the formatting, e.g. rounded corners, does not render on mobile sites.

## Code of Conduct

Please note that the vembedr project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
