---
title: "Helper functions"
author: "Ian Lyttle"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Helper functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
library("htmltools")
library("vembedr")
```

It's a bit inconvenient to visit a service's API page to figure out how do something relatively common, like specify a start time. For this reason a consistent set of helper functions is offered. It is proposed that helper functions used to modify the URL will be called `use_something()` and can be composed using the pipe, `%>%`. At this point, there is one such helper-function: `use_start_time()`.

## Start time

To specify the start time, simply pipe your embed function to the `use_start_time()` function, which figures out which service you are using, then does the "right thing" to modify the query or fragment. 

The `use_start_time()` function will treat these all of these inputs equivalently:

- `"0h1m0s"`, `"0h01m00s"`, `"0h1m"`
- `"1m0s"`, `"1m"`
- `"60s"`, `60`

```{r}
embed_youtube(id = "8SGif63VW6E") %>% 
  use_start_time("4m12s")
```

Hat tip to Aurélien Ginolhac for suggesting this video using this start-time.

The `use_start_time()` function can be used with all of the `embed()` functions. 

### Vimeo caveat

For Vimeo there is one caveat: the specification of start-time causes the video to autoplay without an API recourse to prevent autoplay. Please see this [Vimeo-forum thread](https://vimeo.com/forums/topic:49396) for more informaton.

## Video specification

Let's say you do not have a particular video in mind, but you want to experiment with the arguments and the query parameters. For this set of functions, the video `id` is specified, any argument you provide is passed along to  `embed_youtube()`, `embed_vimeo()`, or `embed_channel9()`.

```{r}
rickroll_youtube()
```

```{r}
rickroll_vimeo()
```

```{r}
rickroll_channel9()
```
