---
title: "Helper functions"
author: "Ian Lyttle"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Helper functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
library("htmltools")
library("vembedr")
```

## Start time

It's a bit inconvenient to visit a service's API page to figure out how do something relatively common, such as specifying a start time. 

Instead, you can pipe the output of your embed function to the `use_start_time()` function, which figures out which service you are using, then does the "right thing" to modify the query or fragment. 

The `use_start_time()` function will treat these all of these inputs equivalently:

- `"0h1m0s"`, `"0h01m00s"`, `"0h1m"`
- `"1m0s"`, `"1m"`
- `"60s"`, `60`

```{r}
embed_youtube(id = "8SGif63VW6E") %>% 
  use_start_time("4m12s")
```

Hat tip to Aurélien Ginolhac for suggesting this video using this start-time.

The `use_start_time()` function can be used with all of the `embed()` functions. 

### Vimeo caveat

For Vimeo there is one caveat: the specification of start-time causes the video to autoplay without an API recourse to prevent autoplay. Please see this [Vimeo-forum thread](https://vimeo.com/forums/topic:49396) for more informaton.

## Suggest code

If you have the URL of the video you want to embed, you can use the `suggest_embed()` function to return to you some suggested code for you to use.

Behind the scenes, the function parses the URL to determine the service, the identifier, and (if applicable) the start time.

### YouTube

You can provide the URL from your browser's address window:

```{r}
suggest_embed("https://www.youtube.com/watch?v=1-vcErOPofQ")
```

You can also provide the URL from the YouTube "Share" button:

```{r}
suggest_embed("https://youtu.be/1-vcErOPofQ?t=28s")
```

### Vimeo

```{r}
suggest_embed("https://vimeo.com/131407894")
```

### Channel 9

This works for the UseR! 2016 videos:

```{r}
suggest_embed("https://channel9.msdn.com/Events/useR-international-R-User-conference/useR2016/Day-3-Siepr-130-Ligtning-Talks-100-PM-140-PM?ocid=player")
```

It also works for the other Channel 9 videos:

```{r}
suggest_embed("https://channel9.msdn.com/Shows/Going+Deep/Brian-Beckman-Dont-fear-the-Monads")
```


## Video specification

Let's say you do not have a particular video in mind, but you want to experiment with the arguments and the query parameters. For this set of functions, the video `id` is specified, any argument you provide is passed along to  `embed_youtube()`, `embed_vimeo()`, or `embed_channel9()`.

```{r}
rickroll_youtube()
```

```{r}
rickroll_vimeo()
```

```{r}
rickroll_channel9()
```
