---
title: "vembedr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vembedr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library("vembedr")
```

Embedding and customizing videos in RMarkdown documents might seem like complex task. 
It need not be.

```{r}
embed_url("https://www.youtube.com/watch?v=_fZQQ7o16yQ") %>%
  use_start_time("1m32")
```

Even the most seemingly-intractable issues can be brought into focus with a clarifying framework.

Above, we used an `embed` function followed by a `use` function.
Using `embed_url()`, you can create an embed object for any of these supported services, or you can use an `id` with a service-specific embed function:

- YouTube: `embed_youtube()`
- Vimeo: `embed_vimeo()`
- Microsoft Channel 9: `embed_channel9()`
- Box: `embed_box()`

You can read more about these services in `vignette("embed")`. 
Once you create an embed object, you can modify it with `use` functions:

- start time: `use_start_time()`
- formatting: `use_align()`, `use_rounded()`
- responsiveness (for Bootstrap): `use_bs_responsive()`

You can read more about these modifications in `vignette("modify")`.

## Examples

To align the video horizontally within its container, `use_align()`:

```{r}
embed_url("https://www.youtube.com/watch?v=uV4UpCq2azs") %>%
  use_align("center")
```

To add rounded corners, `use_rounded()`: 

```{r}
embed_youtube("lGTEUtS5H7I") %>%
  use_rounded()
```

If your HTML file uses Bootstrap, and want to make the size responsive to the width of the container, `use_bs_responsive()`:

```{r}
embed_url("https://www.youtube.com/watch?v=Io2NMCFtqsE") %>%
  use_bs_responsive()
```

For example this **does not** work in the R vignette, but it **does** work in the pkgdown site.

## Caveats

Just because a service publishes a video, this does not mean that you can embed it. 
For example, this is an amazing Otis Redding performance:

```{r}
# does not embed, but you can watch it at Vimeo
embed_vimeo("45157591")
```

Also, as of RStudio 1.3, the RStudio IDE preview window will work with YouTube and Vimeo, but not with Channel 9:

```{r}
rickroll_channel9()
```

If you view this page in a full browser, it should work just fine.


